
\chapter{Introduction}

In cartography, the need to simplify complex geographical data for clear and efficient representation is becoming increasingly important. The rise of automated cartography driven by computer technologies has heightened the demand for efficient algorithms, especially in the areas of feature extraction and simplification.\\

This master thesis aims to contribute to the study of cartographic representation techniques, with a central emphasis on the utilization of PostGIS and MobilityDB \cite{MobilityDBTODS2020}, by exploring solutions for real-time processing of trajectories. Indeed dynamic adaptability is crucial in modern applications such as GPS navigation, real-time geospatial data analysis, and the constant monitoring of geospatial data streams, all of which are integral to the PostGIS and MobilityDB ecosystems.\\

In this study, our primary aim will be to simplify line representations of mobility data within the environment of PostGIS and MobilityDB. This involves the processing of an ordered set of \(n+1\) points in a plane, delineating a polygonal path composed of line segments, and deriving a simplified path with fewer segments while preserving the fundamental attributes of the initial path. Our study stands out for its focus on the real-time nature of the data, which aligns well with the principles and capabilities of PostGIS and MobilityDB.\\

An underlying assumption for this work is the simplicity of the provided path, with an absence of self-intersections. The presence of self-intersections in cartographic data often indicates issues related to digitization errors. While our goal is to keep the resulting approximation simple, the issue of computational feasibility within the PostGIS and MobilityDB environment is a key consideration.\\

The idea of effectively representing data involves several aspects, such as keeping the original and simplified paths close, minimizing the area between them, incorporating critical points from the original path into the simplified one, and optimizing various measures of curve discrepancy. These aspects represent challenges to overcome for an effective real-time trajectory compression algorithm because of the limited information available about the path being processed.\\

\section{Problem Definition}

The problem of simplifying line representations, particularly for mobility data, is a well-known computational challenge that is classified as NP-hard. This means that there is no known polynomial-time algorithm that can solve all instances of this problem optimally. The main objective in line simplification is to reduce the number of points in a path while preserving its essential shape and features. 

Several critical aspects must be considered:

\begin{itemize}
    \item \textbf{Preserving Shape:} The simplified path must retain the general shape and important features of the original path to ensure that the representation remains accurate and meaningful.
    \item \textbf{Minimizing Points:} The goal is to minimize the number of points in the simplified path to reduce data size and computational overhead while maintaining accuracy.
    \item \textbf{NP-Hardness:} The NP-hard nature of the problem implies that exact solutions are computationally infeasible for large datasets. Therefore, heuristic and approximation algorithms are commonly used to provide practical solutions.
    \item \textbf{Accuracy and Error Metrics:} Measures such as the synchronized Euclidean distance (SED), Hausdorff distance, and Fréchet distance are used to quantify the accuracy of the simplified path relative to the original path.
\end{itemize}

These challenges necessitate the development of sophisticated algorithms that can efficiently balance the trade-off between simplification and accuracy.


\section{Objectives of the Thesis}

The main objective of this thesis is to design and implement an efficient algorithm for the simplification of lines representing mobility data, specifically tailored for real-time processing environments using PostGIS and MobilityDB. In detail, the following goals should be achieved:

\begin{itemize}
    \item Design and implement the SQUISH-E algorithm for real-time trajectory simplification.
    \begin{itemize}
        \item Ensure the algorithm minimizes the synchronized Euclidean distance (SED) error while achieving a specified compression ratio.
    \end{itemize}
    
    \item Integrate the SQUISH-E algorithm into PostGIS and MobilityDB.
    \begin{itemize}
        \item Ensure seamless integration and optimal performance within these geospatial database systems.
    \end{itemize}
    
    \item Implement and evaluate the performance of the SQUISH-E algorithm.
    \begin{itemize}
        \item Measure execution time and assess the accuracy of simplified trajectories using metrics such as Hausdorff distance, Fréchet distance, and Dynamic Time Warping.
    \end{itemize}
    
    \item Compare the SQUISH-E algorithm with other existing line simplification algorithms.
    \begin{itemize}
        \item Conduct a detailed comparison with other established algorithms, highlighting improvements in accuracy and computational efficiency.
    \end{itemize}
\end{itemize}

\section{Thesis Structure}

This thesis is structured as follows:

\begin{itemize}
    \item \textbf{Chapter 1: Introduction}
    \begin{itemize}
        \item Introduces the research topic, outlines the objectives, and provides an overview of the thesis structure.
    \end{itemize}
    
    \item \textbf{Chapter 2: State of the Art}
    \begin{itemize}
        \item Reviews the state of the art in line simplification algorithms, real-time processing of geospatial data, and the use of PostGIS and MobilityDB. It provides an overview of existing literature and foundational concepts relevant to this study.
    \end{itemize}
    
    \item \textbf{Chapter 3: Design and Implementation}
    \begin{itemize}
        \item Describes the design and implementation of the SQUISH-E algorithm, including its pseudo-code, data structures, and the integration process into PostGIS and MobilityDB.
    \end{itemize}
    
    \item \textbf{Chapter 4: Experimental Evaluation}
    \begin{itemize}
        \item Presents the experimental evaluation of the SQUISH-E algorithm. It includes performance metrics such as execution time and accuracy, and compares the algorithm with other existing line simplification algorithms.
    \end{itemize}
    
    \item \textbf{Chapter 5: Conclusion}
    \begin{itemize}
        \item Provides the overall conclusions of this work, summarizing the findings, discussing the implications, and suggesting directions for future research.
    \end{itemize}
\end{itemize}




\iffalse
In cartography, the need to simplify complex geographical data for clear and efficient representation is becoming increasingly important. The rise of automated cartography driven by computer technologies has heightened the demand for efficient algorithms, especially in the areas of feature extraction and simplification.\\


This master thesis aims to contribute to the study of cartographic representation techniques, with a central emphasis on the utilization of PostGIS and MobilityDB \cite{MobilityDBTODS2020}, by exploring solutions for real-time processing of trajectories. Indeed dynamic adaptability is crucial in modern applications such as GPS navigation, real-time geospatial data analysis, and the constant monitoring of geospatial data streams, all of which are integral to the PostGIS and MobilityDB ecosystems.\\



In this study, our primary aim will be to simplify line representations of mobility data within the environment of PostGIS and MobilityDB. This involves the processing of an ordered set of n+1 points in a plane, delineating a polygonal path composed of line segments, and deriving a simplified path with fewer segments while preserving the fundamental attributes of the initial path. Our study stands out for its focus on the real-time nature of the data, which aligns well with the principles and capabilities of PostGIS and MobilityDB.\\




An underlying assumption for this work is the simplicity of the provided path, with an absence of self-intersections. The presence of self-intersections in cartographic data often indicates issues related to digitization errors. While our goal is to keep the resulting approximation simple, the issue of computational feasibility within the PostGIS and MobilityDB environment is a key consideration.\\




The idea of effectively representing data involves several aspects, such as keeping the original and simplified paths close, minimizing the area between them, incorporating critical points from the original path into the simplified one, and optimizing various measures of curve discrepancy. These aspects represent challenges to overcome for an effective real-time trajectory compression algorithm because of the limited information available about the path being processed.\\



\subsection{Definitions and Key Concepts}
In this subsection, we will establish a foundational understanding of key terms and concepts central to the research presented in this thesis. These definitions are essential for comprehending the context and significance of the study.

\subsubsection{Moving Objects}

Moving objects refer to entities or points that continuously change their positions in a given space over time. In the context of this research, moving objects represent dynamic or mobile assets, including vehicles, individuals, or any entities with ever-changing spatial coordinates. Understanding the behavior of moving objects is fundamental for the stream algorithm proposed in this study.

\subsubsection{Stream Data}

Stream data pertains to the continuous and real-time flow of data that arrives sequentially. In the context of this research, stream data represents the dynamic nature of the information being processed. Stream data includes data points, such as the changing positions of moving objects, which are received and processed as they become available over time.


\subsubsection{Polygonal Path}

A polygonal path is a sequence of line segments connected end-to-end, forming a coherent trajectory or route. In the context of this research, a polygonal path represents the course taken by moving objects, represented as a series of line segments, which is the primary focus of the stream algorithm for simplification.


\subsubsection{Restricted Version}

A restricted version in this context signifies a specialized or limited form of an algorithm or problem. It is tailored to accommodate specific constraints or requirements pertinent to the application. For example, a restricted version of a line simplification algorithm may be designed to address particular limitations associated with moving objects and streaming data.



\subsubsection{Function Error}

Function error indicates the degree of discrepancy between an ideal or reference function and an approximation or simplified representation. In the context of line simplification, it quantifies the degree to which the simplified line retains the essential characteristics of the original polygonal path.

\subsubsection{Fréchet Distance}

The Fréchet distance is a distance metric that quantifies the similarity between two curves or paths. It measures the likeness between the original polygonal path and a simplified path by considering the minimum separation distance between a moving object on each path as they traverse from start to end.


\subsubsection{The Hausdorff Distance}

The Hausdorff distance is another distance metric used to measure the similarity or dissimilarity between two sets or paths. It calculates the maximum distance from each point in one set to the nearest point in the other set, providing a measure of the dissimilarity between paths.


\subsubsection{Convex Paths}

Convex paths represent polygonal paths with the property that any line segment connecting two points lies entirely within the convex hull of the points. Convex paths exhibit certain geometric properties that can be advantageous in the context of simplification algorithms.

\subsubsection{XY-Monotone Paths}

An XY-monotone path is a polygonal path with the characteristic of being monotonic in both the x and y directions. Such paths move in one direction along the x and y axes without backtracking.

\subsubsection{General Paths}

General paths encompass polygonal paths without specific constraints on their geometry. They may exhibit complex shapes, including non-monotonic behavior, sharp turns, and diverse geometric characteristics.

\fi
